Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-25 arxiv-version/main.tex
Add references and start another section

We design new algorithms for the problem of \textsc{Online Multiclass
Classification with Bandit Feedback}. In this problem, in each round, the
algorithm receives a feature vector and the algorithm has to predict one of $K$
possible classes. Imediately after the algorithm makes its prediction, it
receives feedback whether the prediction was correct or not. However, in
contrast with the standard, so called full information setting, the algorithm
does \emph{not} receive the correct label. The feedback is only binary. To allow
for meaningful randomized strategies, we assume that the correct label in a
particular round is chosen prior to algorithm's prediction in that
round.\footnote{The reader can assume throughout the paper a simpler model of
the so called \emph{oblivious adversary} where the whole sequence of labeled
examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
round of the game.} The protocol of the problem is stated below.

@@

@@

\section{Converting linear separability to strong linear separability}

@@

A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
linearly separate the examples see in previous rounds and use the vectors to
predict label in the next round. More precisely, we want to find both the
vectors $w_1, w_2, \dots, w_K$ and label for each exaple consistent with its
weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
labeled examples. We show this problem is NP-hard even for $K=3$.

@@

It remains to show that the examples we have constructed are linearly separable
with margin $\gamma$. To prove that we demostrate vectors $w_1, w_2, \dots, w_K$
satisfying conditions \eqref{equation:linear-separability-1} and
\eqref{equation:linear-separability-2}. We define
$$
w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
$$
Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurences of label $i$.
It is easy to see that
$$
\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
$$
Since $\sum_{i=1}^K a_i = T$, the condition
\eqref{equation:linear-separability-1} holds. To verify condition
\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
y_t)$. Then, by definition of $w_{y_t}$ we have
$$
\ip{w_{y_t}}{x_t}
= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
= \frac{1}{R\sqrt{T}} \norm{x_t}^2
= \frac{R}{\sqrt{T}}
\ge \frac{R}{R/\gamma}
= \gamma \; .
$$
and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
\end{proof}

>>>>

We design new algorithms for the problem of \textsc{Online Multiclass
Classification with Bandit Feedback}. In this problem, in each round, the
algorithm receives a feature vector and the algorithm has to predict one of $K$
possible classes. Immediately after the algorithm makes its prediction, it
receives feedback whether the prediction was correct or not. However, in
contrast with the standard, so called full information setting, the algorithm
does \emph{not} receive the correct label. The feedback is only binary. To allow
for meaningful randomized strategies, we assume that the correct label in a
particular round is chosen prior to algorithm's prediction in that
round.\footnote{The reader can assume throughout the paper a simpler model of
the so called \emph{oblivious adversary} where the whole sequence of labeled
examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
round of the game.} The protocol of the problem is stated below.

@@

\cite{Abernethy-Rakhlin-2009}

\cite{Hazan-Kale-2011}

\cite{Foster-Krishnamurthy-2018}

@@

\section{Converting linear separability to strong linear separability}
\label{section:converting-linear-separability-to-strong-linear-separability}

In this section, we show how construct a mapping $\phi$ of points in the unit
ball $B_d$ of $\R^d$ into a high dimensional inner product space that has the
property if any set of labeled examples in $B_d$ is linearly separable with a
margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
the number of classes $K$, and the are specified in the theorems below.

Equipped with the mapping $\phi$, we can utilize
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
previous section and we obtain an algorithm for linearly separable examples and
an upper bound on its number of mistakes. As a computational speed up, instead
of working with the mapped examples $\phi(x_1), \phi(x_2), \dots$ explicitly, we
can use the kernelized version of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
that uses a kernel function $k(x,x') = \ip{\phi(x)}{\phi(x')}$.

We construct several different mappings $\phi$. The parameters $R'$ and
$\gamma'$ for the different mappings are essentially the same. However, one
mapping has the advantage of having a kernel $k(x,x')$ that is faster to
evaluate. Another mapping has the advantage that one does \emph{not} need to
know the initial margin $\gamma$. In other words, the same mapping works for all
possible values of $\gamma > 0$. The idea behind all the mappings is that
polynomials are universal function approximators, which is a well known fact
expressed by the classical Stone-Weierstrass theorem~\citep[page 159]{Rudin-1976}.

\subsection{Polynomials}
TODO

\subsection{Rational Kernel}
TODO

@@

A natural strategy for each round is to find vectors $w_1, w_2, \dots, w_K$ that
linearly separate the examples seen in the previous rounds and use the vectors
to predict the label in the next round. More precisely, we want to find both the
vectors $w_1, w_2, \dots, w_K$ and label for each example consistent with its
weak and/or strong labels such that $w_1, w_2, \dots, w_K$ linearly separate the
labeled examples. We show this problem is NP-hard even for $K=3$.

@@

It remains to show that the examples we have constructed are linearly separable
with margin $\gamma$. To prove that we demonstrate vectors $w_1, w_2, \dots, w_K$
satisfying conditions \eqref{equation:linear-separability-1} and
\eqref{equation:linear-separability-2}. We define
$$
w_i = \frac{1}{R\sqrt{T}} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} x_t \qquad \qquad \text{for $i=1,2,\dots,K$.}
$$
Let $a_i = |\{ t ~:~ 1 \le t \le T, \ y_t = i \}|$ be the number of occurrences of label $i$.
It is easy to see that
$$
\norm{w_i}^2 = \frac{1}{R^2 T} \sum_{\substack{t : 1 \le t \le T \\ y_t = i}} \norm{x_t}^2 = \frac{a_i}{T} \qquad \qquad \text{for $i=1,2,\dots,K$.}
$$
Since $\sum_{i=1}^K a_i = T$, the condition
\eqref{equation:linear-separability-1} holds. To verify condition
\eqref{equation:linear-separability-2} consider any labeled example $(x_t,
y_t)$. Then, by definition of $w_{y_t}$ we have
$$
\ip{w_{y_t}}{x_t}
= \frac{1}{R\sqrt{T}} \sum_{\substack{s : 1 \le s \le T \\ y_s = y_t}} \ip{x_s}{x_t}
= \frac{1}{R\sqrt{T}} \norm{x_t}^2
= \frac{R}{\sqrt{T}}
\ge \frac{R}{R/\gamma}
= \gamma \; .
$$
and for any $i \in \{1,2,\dots,K\} \setminus \{y_t\}$ we have
$\ip{w_i}{x_t} = 0$. Therefore, condition \eqref{equation:linear-separability-2} holds.
\end{proof}
